\documentclass{article}

\begin{document}

\title{LINUX}
\author{JOHN BWALE}
\date{TODAY}

\maketitle

\section{  Linux Programing Shell, navigation - Task 2 }
\textbf{Q1:} Which command should you use to display the current path of your current directory? \\
\textbf{A1:} The command you should use to display the current path of your current directory is \texttt{pwd}.

\textbf{Q2:} Which command should you use to change directory? \\
\textbf{A2:} The command you should use to change directory is \texttt{cd}.

\textbf{Q3:} Which command should you use to display the content of a file? \\
\textbf{A3:} The command you should use to display the content of a file is \texttt{less}.

\textbf{Q4:} Which command should you use to create an empty file? \\
\textbf{A4:} The command you should use to create an empty file is \texttt{touch}.

\textbf{Q5:} Which command should you use to copy a file (or directory if additional argument)? \\
\textbf{A5:} The command you should use to copy a file (or directory if additional argument) is \texttt{cp}.

\textbf{Q6:} Which command should you use to rename or move a file (or directory)? \\
\textbf{A6:} The command you should use to rename or move a file (or directory) is \texttt{mv}.

\textbf{Q7:} Which command should you use to delete a file (or directory if additional argument)? \\
\textbf{A7:} The command you should use to delete a file (or directory if additional argument) is \texttt{rm}.

\textbf{Q8:} Which command should you use to create a directory? \\
\textbf{A8:} The command you should use to create a directory is \texttt{mkdir}.

\textbf{Q9:} Which command should you use to delete a directory? \\
\textbf{A9:} The command you should use to delete a directory is \texttt{rmdir}.

\end{document}