\documentclass{article}

\begin{document}

\section*{Quiz Questions (Contd.)}

\begin{enumerate}
  \item The purpose of the \texttt{fg} command is:
  \begin{enumerate}
    \item A. to open the floodgates
    \item B. to show the number of free gates
    \item C. to send the given process into the State Fairgrounds
    \item D. to put the given job into the foreground
  \end{enumerate}
  Correct answer: \textbf{D. to put the given job into the foreground}
  
  \item To change a file’s permissions, giving read and execute permission to the user/owner, what option would be given to the \texttt{chmod} command?
  \begin{enumerate}
    \item A. \texttt{o-rx}
    \item B. \texttt{o+rx}
    \item C. \texttt{u+rx}
    \item D. \texttt{u-rw}
  \end{enumerate}
  Correct answer: \textbf{C. \texttt{u+rx}}
  
  \item Why is it important to sometimes use the \texttt{-9} flag with the \texttt{kill} command?
  \begin{enumerate}
    \item A. It tells \texttt{kill} to end all processes associated with the current shell.
    \item B. It tells \texttt{kill} to find and kill the process using the most memory.
    \item C. It tells \texttt{kill} to end all processes in the system.
    \item D. It tells \texttt{kill} to force the process to end, even if it is not cooperating.
  \end{enumerate}
  Correct answer: \textbf{D. It tells \texttt{kill} to force the process to end, even if it is not cooperating.}
  
  \item Which of these commands will end a process?
  \begin{enumerate}
    \item A. \texttt{kill}
    \item B. \texttt{end}
    \item C. \texttt{stop}
    \item D. \texttt{terminate}
  \end{enumerate}
  Correct answer: \textbf{A. \texttt{kill}}
  
  \item To change a file’s permissions, removing write permission from all users, what option would be given to the \texttt{chmod} command?
  \begin{enumerate}
    \item A. \texttt{g-w}
    \item B. \texttt{w-w}
    \item C. \texttt{a-w}
    \item D. \texttt{u-w}
  \end{enumerate}
  Correct answer: \textbf{C. \texttt{a-w}}
  
  \item Which of these commands is used to change permissions on files and directories?
  \begin{enumerate}
    \item A. \texttt{modch}
    \item B. \texttt{allow}
    \item C. \texttt{perm}
    \item D. \texttt{chmod}
  \end{enumerate}
  Correct answer: \textbf{D. \texttt{chmod}}
  
  \item Which of these commands is used to send a job to the background?
  \begin{enumerate}
    \item A. \texttt{ps}
    \item B. \texttt{bg}
    \item C. \texttt{fg}
    \item D. \texttt{jobs -bg}
  \end{enumerate}
  Correct answer: \textbf{B. \texttt{bg}}
  
  \item Which of these commands shows the correct way to start a program as a background job?
  \begin{enumerate}
    \item A. \texttt{bg ./program.py}
    \item B. \texttt{fg ./program.py}
    \item C. \texttt{bg ./program.py \&}
    \item D. \texttt{./program.py \&}
  \end{enumerate}
  Correct answer: \textbf{C. \texttt{bg ./program.py \&}}
  
  \item We need to stop the current foreground job! What should we type?
  \begin{enumerate}
    \item A. \texttt{Ctrl-Y}
    \item B. \texttt{Ctrl-Z}
    \item C. \texttt{Ctrl-Q}
    \item D. \texttt{Ctrl-X}
  \end{enumerate}
  Correct answer: \textbf{B. \texttt{Ctrl-Z}}
  
  \item Which of these commands will display a list of all processes on the system?
  \begin{enumerate}
    \item A. \texttt{ps -f}
    \item B. \texttt{ps -A}
    \item C. \texttt{ps -all}
    \item D. \texttt{ps}
  \end{enumerate}
  Correct answer: \textbf{B. \texttt{ps -A}}
  
  \item The purpose of the \texttt{jobs} command is to:
  \begin{enumerate}
    \item A. list all jobs within the current shell
    \item B. create new jobs within the current shell
    \item C. list only stopped jobs within the current shell
    \item D. list only running jobs within the current shell
  \end{enumerate}
  Correct answer: \textbf{A. list all jobs within the current shell}
  
\end{enumerate}

\end{document}
