\documentclass{article}

\begin{document}

\section*{Quiz Questions}

\begin{enumerate}
    \item A bash shell script should begin with which two characters?
    \begin{enumerate}
        \item A. /!
        \item B. \#! (hash exclamation mark)
        \item C. \%\%
        \item D. \#/
    \end{enumerate}
    Correct answer: \textbf{B. \#! (hash exclamation mark)}

    \item Which of the following is a correct interpreter directive for bash?
    \begin{enumerate}
        \item A. \#!/etc/bash
        \item B. \#!/bin/bash
        \item C. \#!/bin/sh
        \item D. \#!/home/jokane/bin/bash
    \end{enumerate}
    Correct answer: \textbf{B. \#!/bin/bash}

    \item What is the purpose of the special variables $1, $2, ...?
    \begin{enumerate}
        \item A. To refer to the previous commands executed in the shell
        \item B. To refer to arguments given on the command line to a script
        \item C. To refer to the parent directories of the current directory
        \item D. To refer to the other users logged in to the system
    \end{enumerate}
    Correct answer: \textbf{B. To refer to arguments given on the command line to a script}

    \item Which of these commands prints the value of the variable QUUX?
    \begin{enumerate}
        \item A. show QUUX
        \item B. echo \$QUUX
        \item C. echo QUUX
        \item D. cat \$QUUX
    \end{enumerate}
    Correct answer: \textbf{B. echo \$QUUX}

    \item Which of the following steps is not necessary to make a file containing commands usable as a bash shell script?
    \begin{enumerate}
        \item A. Compiling the file into an executable using a bash compiler.
        \item B. Putting the file in a place where the shell can find it.
        \item C. Making the file executable.
        \item D. Specifying the interpreter using an interpreter directive.
    \end{enumerate}
    Correct answer: \textbf{A. Compiling the file into an executable using a bash compiler.}

    \item Which of these commands assigns a value to the shell variable FOO?
    \begin{enumerate}
        \item A. FOO=bar
        \item B. bar -> foo
        \item C. bar->foo
        \item D. foo =bar
    \end{enumerate}
    Correct answer: \textbf{A. FOO=bar}

    \item Which environment variable contains a list of directories that should be searched for programs to execute?
    \begin{enumerate}
        \item A. SHELL
        \item B. SEARCH
        \item C. PWD
        \item D. PATH
    \end{enumerate}
    Correct answer: \textbf{D. PATH}

    \item Which of the following commands declares that the variable QUUZ should be available to subprocesses launched by this shell?
    \begin{enumerate}
        \item A. subproc QUUZ
        \item B. global QUUZ
        \item C. export QUUZ
        \item D. shipout QUUZ
    \end{enumerate}
    Correct answer: \textbf{C. export QUUZ}

    \item Which of the following shell features can be used in a shell script?
    \begin{enumerate}
        \item A. pipes
        \item B. output redirection
        \item C. input redirection
        \item D. all of the above
    \end{enumerate}
    Correct answer: \textbf{D. all of the above}

    \item The PATH variable is a list of directories, separated by:
    \begin{enumerate}
        \item A. periods (.)
        \item B. commas (,)
        \item C. colons (:)
        \item D. semicolons (;)
    \end{enumerate}
    Correct answer: \textbf{C. colons (:)}
\end{enumerate}

\end{document}
